### 2016-07-31 Projects/DelCo_2012/Report/DelCo_2012.tex
fix caf typos

Note that while there are some differences in the changes in temperature and heat flux when comparing CAF to Water, the differences are not substantial. Both suppression agents had similar, significant impacts in reducing the high-temperature, high-heat flux environment that existed before suppression. The first (hallway) suppression, an indirect attack, did a majority of the cooling in all of the tests. This illustrates the impact of gas cooling, independent of suppression agent. In several cases rekindling occurred, as seen by the temperature increase between the two nozzle applications, but all cases the second (room) attack controlled the fire.  However in most cases rekindling occured as nozzle movement was needed to completely extinguish the fire.

@@

In all of the suppression experiments, the fire was controlled with total flow of 227~L (60~gal) or less of agent. During the course of the suppression experiments the fuel packages were modified to incorporate more wood-based fuels. During the planning of the experiments, some of the technical panel members felt that the synthetic fuels, such as polyurethane foam, burned mostly at the surface and therefore they were easily cooled and suppressed. Wood-based fuels, on the otherhand, develop a char layer and therefore the burning would be ``deep seated'', which might provide a more significant suppression challenge. Since the Class A foam solution has a reduced surface tension, that could allow the solution to penetrate and cool the burning wood-based fuels better, it was thought that with more exposed, burning wood surface, the better the opportunity for CAF to demonstrate a difference. As shown in Chapter~\ref{sec:fuel_load}, the wood fuel load consisted of stacks of wood pallets, plywood lined walls, and an exposed wood ``ceiling'' that was constructed of wood ``i-beams'' and oriented strand board. The experiments conducted with the wood fuel load did not demonstrate a significant difference between water and CAF.

>>>>

Note that while there are some differences in the changes in temperature and heat flux when comparing CAF to Water, the differences are not substantial. Both suppression agents had similar, significant impacts in reducing the high-temperature, high-heat flux environment that existed before suppression. The first (hallway) suppression, an indirect attack, did a majority of the cooling in all of the tests. This illustrates the impact of gas cooling, independent of suppression agent. In several cases rekindling occurred, as seen by the temperature increase between the two nozzle applications, but all cases the second (room) attack controlled the fire.  However in most cases rekindling occurred as nozzle movement was needed to completely extinguish the fire.

@@

In all of the suppression experiments, the fire was controlled with total flow of 227~L (60~gal) or less of agent. During the course of the suppression experiments the fuel packages were modified to incorporate more wood-based fuels. During the planning of the experiments, some of the technical panel members felt that the synthetic fuels, such as polyurethane foam, burned mostly at the surface and therefore they were easily cooled and suppressed. Wood-based fuels, on the other hand, develop a char layer and therefore the burning would be ``deep seated'', which might provide a more significant suppression challenge. Since the Class A foam solution has a reduced surface tension, that could allow the solution to penetrate and cool the burning wood-based fuels better, it was thought that with more exposed, burning wood surface, the better the opportunity for CAF to demonstrate a difference. As shown in Chapter~\ref{sec:fuel_load}, the wood fuel load consisted of stacks of wood pallets, plywood lined walls, and an exposed wood ``ceiling'' that was constructed of wood ``i-beams'' and oriented strand board. The experiments conducted with the wood fuel load did not demonstrate a significant difference between water and CAF.
